A Topography of Climate Change Research

### 2018-02-12 pres/2018_02_pres.tex
literature volume bitbybit

@@

\only<1->{\includegraphics[]{C:/Users/galm/Documents/papers/sustainability/plots/VWH_1991}}
\only<2->{\includegraphics[]{C:/Users/galm/Documents/papers/sustainability/plots/VWH_1992}}

\only<3->{\includegraphics[]{C:/Users/galm/Documents/papers/sustainability/plots/VWH_1993}}

>>>>

\begin{frame}{Data - IPCC References}
	\textbf{Matching process}

	\medskip

	For each Reference:
	\begin{itemize}
		\item Check for case-insensitive title matches
		\item Calculate the Jaccard similarity score for two word every database document containing the first word and from the same year. Match if the Jaccard score is above 0.45
	\end{itemize}
\end{frame}

\begin{frame}{Data - IPCC References}
%\begin{columns}
	%\begin{column}{0.5\linewidth}
		\includegraphics[width=\linewidth]{../plots/ipcc_matches}
	%\end{column}
%\end{columns}
\end{frame}

\begin{frame}{Data - Unmatched IPCC References}
	\tiny
	\input{../tables/ipcc_matching_sample.tex}
\end{frame}

\begin{frame}{Data - Unmatched IPCC References}

37\% of IPCC References could be matched to the database of climate-relevant documents

\medskip

\textbf{Reasons for not matching}
\begin{enumerate}
	\item<2->Reference is not in WoS (not peer-reviewed, in minor journal)
	\item<3->Reference is not directly about climate change
	\item<4->Reference has been incorrectly parsed
\end{enumerate}

\medskip

\textbf{Observations}
\begin{itemize}
	\item<5-> The size of the literature appears to be \textit{much} bigger than our estimate
	\item<6-> WG3 refers to more literature not directly about climate change, or not in peer-reviewed publications, than WG2, which refers to more than WG1
\end{itemize}

@@

\only<1->{\includegraphics[]{../plots/sustainability/VWH_1991}}
\only<2->{\includegraphics[]{../plots/sustainability/VWH_1992}}

\only<3->{\includegraphics[]{../plots/sustainability/VWH_1993}}
